Iterative construction of replicated designs based on Sobol' sequences

### 2016-05-30 crass/crass.tex
changes crass.tex + graphes

% The amssymb package provides various useful mathematical symbols
\usepackage{amsmath,amssymb}

@@

\newcommand{\fudge}{\fC}
\newcommand{\dtf}{\textit{\doubletilde{f}}}
\newcommand{\cube}{[0,1)^s}
\newcommand{\rf}{\mathring{f}}
\newcommand{\rnu}{\mathring{\nu}}
\newcommand{\natm}{\naturals_{0,m}}
\newcommand{\wcS}{\widecheck{S}}
\newcommand{\tol}{\text{tol}}
\newcommand{\bvec}[1]{\boldsymbol{#1}}
\newcommand{\vx}{\bvec{x}}
\newcommand{\vi}{\bvec{i}}
\newcommand{\vj}{\bvec{j}}
\newcommand{\ve}{\bvec{e}}
\newcommand{\vk}{\bvec{k}}
\newcommand{\vz}{\bvec{z}}
\newcommand{\dif}{\mathsf{d}}
\newcommand{\hf}{\hat{f}}
\newcommand{\hS}{\widehat{S}}
\newcommand{\tS}{\widetilde{S}}
\newcommand{\tf}{\tilde{f}}
\newcommand{\fC}{\mathfrak{C}}
\newcommand{\homega}{\widehat{\omega}}
\newcommand{\wcomega}{\mathring{\omega}}
\newcommand{\vzero}{\bvec{0}}
\newcommand{\integers}{\mathbb{Z}}
\newcommand{\naturals}{\mathbb{N}}
\newcommand{\ip}[3][{}]{\ensuremath{\left \langle #2, #3 \right \rangle_{#1}}}

@@

% use the thanksref command within \title, \author or \address for footnotes;
% use the ead command for the email address,
% and the form \ead[url] for the home page:
% \title{Title\thanksref{label1}}
% \thanks[label1]{}
% \author{Name\thanksref{label2}}
% \ead{email address}
% \ead[url]{home page}
% \thanks[label2]{}
% \address{Address\thanksref{label3}}
% \thanks[label3]{}
\selectlanguage{english}
\title{Construction of replicated designs based on Sobol' sequences}
%\title{Replicated designs based on Sobol' sequences to estimate main effects of model inputs}
%\title{On the replication of Sobol' sequences to estimate main effects of model inputs}

@@

\begin{abstract}
\selectlanguage{english}
% Text of abstract in English
In the perspective of estimating main effects of model inputs, two approaches are studied to construct replicated designs based on Sobol' sequences.
{\it To cite this article: L.
Gilquin, Ll. A. Jim\'enez Rugama, E. Arnaud, F. J. Hickernell, H. Monod, C. Prieur, C. R. Acad. Sci. Paris, Ser. I 340 (2005).}

@@

\selectlanguage{francais}
% Text of abstract in French
\noindent{\bf R\'esum\'e} \vskip 0.5\baselineskip \noindent
{ \bf Construction de plans r\'epliqu\'es \`a partir de s\'equences de Sobol'.}
%{\bf Plans r\'epliqu\'es \`a base de s\'equences de Sobol' pour estimer les effets principaux des param\`etres d'un mod\`ele. }
Dans le contexte d'estimer les effets principaux des param\`etres d'un mod\`ele, nous proposons d'\'etudier deux approches pour construire des plans r\'epliqu\'es \`a partir de s\'equences de Sobol'.
{\it Pour citer cet article~: L. Gilquin, Ll. A. Jim\'enez Rugama, E. Arnaud, F. J. Hickernell, H. Monod, C. Prieur, C. R. Acad. Sci.
Paris, Ser. I 340 (2005).}

@@

\section{Introduction}
Mathematical models often involve a substantial number of poorly known parameters. The effect of these parameters to the output of the model can be assessed through sensitivity analysis. Global sensitivity analysis methods are useful tools to identify the parameters having the most influence on the output. A well known approach is the variance based method introduced by Sobol' in \cite{Sobol2}. This method estimates sensitivity indices called Sobol' indices that summarize the influence of each model input. In particular, one can distinguish first-order indices that estimate the main effect of each input.

The procedure proposed by Sobol' to estimate first-order Sobol' indices and its improvements (see Saltelli \cite{Saltelli} for an exhaustive survey) suffer from a prohibitive cost of model evaluations that grows with respect to the input space dimension. %An elegant solution to reduce this cost relies on the construction of replicated designs introduced by McKay \cite{mckay}.  
 An elegant solution to reduce this cost relies on the construction of particular design of experiments called replicated designs. The notion of replicated designs was first introduced by McKay through its introduction of replicated Latin Hypercubes in \cite{Mckay}. 
Below we define replicated designs in a wider framework:

\begin{definition}%[Replicated designs]
\label{rep.designs}
Denote by $\vx \in [0,1)^s$ a point with components $x_1,\dots,x_s$ and $\mathcal{D}=\{1,\dots,s\}$. Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in
$[0,1)^{s}$. Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp. $\mathcal{P}'^u$), $u \subsetneq \mathcal{D}$, denote the subset of dimensions of $\mathcal{P}$ (resp. $\mathcal{P}'$) indexed by $u$. We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a$ if $\forall \ u \subsetneq \mathcal{D}$ such that $|u|=a$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ are the same point set in $[0,1)^a$.
\end{definition}

The replication procedure introduced by \cite{Mara,Tissot} allows to estimate all first-order Sobol' indices with only two replicated designs of order $1$. This procedure has the major advantage of reducing the estimation cost as the number of model evaluations (one design $\mathcal{P}$ of size $n$  and its replication $\mathcal{P}'$) becomes independent of the input space dimension. However, Sobol' indices estimates may still not be accurate enough if the input space is not properly explored.
\bigskip

In this note, we propose the construction of two replicated point sets based on Sobol' sequences that identify as two space-filling replicated designs of order $1$. These two designs ensure that the input space is properly explored and can be used within the replication procedure to estimate all main-effects of a numerical model. We first provide a brief introduction on digital sequences and then present two iterative approaches to construct the two replicated point sets.

@@

The quality of any $(t,m,s)$-net or $(t,s)$-sequence is measured by $t$, called the $t$-value. The $t$-value is introduced in the $(t,m,s)$-net definition as follows:

@@

Thus, a $(t,m,s)$-net is defined such that all elementary intervals of volume at least $b^{t-m}$ will enclose a proportional number of points of $\mathcal{P}$, namely $b^{t-m}|\mathcal{P}|$ points. The most evenly spread nets are $(0,m,s)$-nets, since each elementary interval of the smallest volume possible, $b^{-m}$, contains exactly one point.

@@

$s$-dimensional Sobol' sequences are designed in base $b=2$ and can be computed using the \emph{generating matrices}, a set of $s$ full rank infinite dimensional upper triangular matrices over $\mathbb{F}_2:=\{0,1\}$. We will denote by $\oplus$ the addition in $\mathbb{F}_2:=\{0,1\}$. In \cite{Kuo}, Kuo  and Joe suggest a particular choice for these matrices that optimize the 2 dimensional projection $t$-values.

Consider the generating matrices $C_1,\dots,C_s$, and $C_1^m,\dots,C_s^m$ their upper left corner blocks of size $m\times m$. Although $C_1,\dots,C_s$ are of infinite size, one only requires the knowledge of $C_1^m,\dots,C_s^m$ to construct the first $2^m$ points: for each $i=0,\dots,2^m-1$, the point $\vx_i = (x_{i,1},\dots,x_{i,s})^\intercal$ of the sequence is obtained dimension-wise:
\begin{equation}
\label{dig.net.eq.}
(x_{i,j,1},\dots,x_{i,j,m})^\intercal = C_j^{m} \vi,\qquad j= 1,\dots,s\, ,
\end{equation}
where $x_{i,j} = \sum_{k \geq 1}x_{i,j,k}2^{-k}$ and $\vi = (i_{0},\dots,i_{m-1})^\intercal$ are the binary decompositions of $x_{i,j}$ and $i$, and matrix operations are performed in $\mathbb{F}_2$. Below we provide an example on how to compute $x_{11,1}=0.8125$ and $x_{9,2}=0.4375$,
\begin{equation*}
\begin{pmatrix}
x_{11,1,1} \\
x_{11,1,2} \\
x_{11,1,3} \\
x_{11,1,4}
\end{pmatrix} = 
\overbrace{
\begin{pmatrix}
1 & 0 & 0 & 0 \\
0 & 1 & 0 & 0 \\
0 & 0 & 1 & 0 \\
0 & 0 & 0 & 1
\end{pmatrix}}^{C_1^4}
\overbrace{
\begin{pmatrix}
1 \\
1 \\
0 \\
1
\end{pmatrix}}^{\bvec{11}}=
\begin{pmatrix}
1 \\
1 \\
0 \\
1
\end{pmatrix}
,\qquad
\begin{pmatrix}
x_{9,2,1} \\
x_{9,2,2} \\
x_{9,2,3} \\
x_{9,2,4}
\end{pmatrix} = 
\overbrace{\begin{pmatrix}
1 & 1 & 1 & 1 \\
0 & 1 & 0 & 1 \\
0 & 0 & 1 & 1 \\
0 & 0 & 0 & 1
\end{pmatrix}}^{C_2^4}
\overbrace{\begin{pmatrix}
1 \\
0 \\
0 \\
1
\end{pmatrix}}^{\bvec{9}} =
\begin{pmatrix}
0 \\
1 \\
1 \\
1
\end{pmatrix}
\end{equation*}
\bigskip

To compute the next $2^m$ points of the sequence, one can infer from equation (\ref{dig.net.eq.}) that \\$(x_{i+2^m,j,1},\dots,x_{i+2^m,j,m+1})^\intercal=(x_{i,j,1},\dots,x_{i+2^m,j,m},0)^\intercal\oplus {(c_j^{m+1})}^\intercal$, where $c_j^{m+1}$ is the last column of $C_j^{m+1}$.

\begin{lemma}\label{Sobol_replicated}
All Sobol' sequences are digitally replicated of order 1.
\end{lemma}
\begin{pf*}{Proof.}
Consider any two $s$-dimensional Sobol' sequences generated by $C_1,\dots,C_s$ and $C'_1,\dots,C'_s$ respectively. Since any two matrices $C^{m}_j$ and ${C'}^{m}_j$ are square and full rank, the operations $C^{m}_j\vi$ and ${C'}^{m}_j\vi$ are one-to one and onto for all $i=0,\dots,2^m-1$. Therefore, they generate the same point sets.
\end{pf*}

@@

\section{Iterative constructions of extensible replicated point sets of order 1}

In this section we propose two different approaches to construct extensible replicated point sets of order 1, $\mathcal{P}_m$ and $\mathcal{P}'_m$, based on Sobol' sequences. These two constructions are iteratively extended according to:
$$\mathcal{P}_m= B_0 \cup \dots \cup B_m\, ,$$
$$\mathcal{P}'_m= {B'}_0 \cup \dots \cup {B'}_m\, ,$$
where $B_m$ and $B'_m$, $m \geq 0$, are new sets of points added at step $m$ to refine $\mathcal{P}_{m-1}$ and $\mathcal{P}'_{m-1}$. For all $m$, $\mathcal{P}_m$ and $\mathcal{P'}_m$ are two replicated designs of order $1$.

The first approach is called multiplicative because $|P_m|=2^m$ while the second one with $|P_m|=m|B_0|$ is called additive. In the multiplicative case, we will directly use $2$ $s$-dimensional sequences as a result from Lemma \ref{Sobol_replicated}. However, for the additive case, we will consider an initial set of Sobol' points and apply different scramblings and digital shifts to extend the point sets. Additionally, in both cases one can randomize the points with Owen's scrambling \cite{OwenScrambling} as long as equal dimensions between $\mathcal{P}_m$ and $\mathcal{P}'_m$ share the same scrambling.

@@

Two replicated point sets of order 1 $\mathcal{P}_m$ and $\mathcal{P}'_m$ can be constructed using two $s$-dimensional Sobol' sequences. We note $C_1,\dots,C_s$ the generating matrices used to generate $\mathcal{P}_m$ and ${C'}_1,\dots,{C'}_s$ those used to generate $\mathcal{P}'_m$. All these matrices need to be different.
% Our choice of the $2s$ generating matrices $C_1,\dots,C_s,{C'}_1,\dots,{C'}_s$ follows the results obtained by Joe and Kuo in \cite{Kuo}. These two authors proposed a set of generating matrices optimized based on the $t$-value of pairwise projections of the corresponding digital sequence. Here, we select $2s$ generating matrices from this set to generate our two designs $\mathcal{P}$ and $\mathcal{P}'$.
\bigskip

In order to iteratively construct designs $\mathcal{P}_m$ and $\mathcal{P}'_m$, one just needs to compute $B_\ell=\{\vx_{2^{\ell-1}},\dots,\vx_{2^\ell-1}\}$ and ${B'}_\ell=\{\vx'_{2^{\ell-1}},\dots,\vx'_{2^\ell-1}\}$ for all $\ell=1,\dots,m$, with $B_0=B'_0=\{\bvec{0}\}$. Each set $B_\ell$ can be obtained applying equation (\ref{dig.net.eq.}) to $C_1,\dots,C_s$, and $B'_\ell$ using $C'_1,\dots,C'_s$.

@@

With the multiplicative approach, the size of designs $\mathcal{P}_m$ and $\mathcal{P}'_m$ is multiplied by $2$ each time $m$ is increased by one. This growth rate may be inadequate for some applications. The additive approach presented in this section is attractive due to a slower size growth. Given a particular choice of $r\geq 1$, only $|B_0|=2^r$ points are added to both designs at each step. However, the main drawback is that $\mathcal{P}_m$ and $\mathcal{P}'_m$ do not possess the structure of a Sobol' sequence when $m\geq 1$.
\bigskip

The two replicated point sets $\mathcal{P}_m$ and $\mathcal{P}'_m$ constructed with the additive approach are iteratively refined with $B_{m+1}$ and ${B'}_{m+1}$. Each $B_{m+1}$ and ${B'}_{m+1}$ are $(t,r,s)$-nets.

First, $B_0=\{\vx_i^{(0)}\}_{i=0}^{2^r-1}$ is set to be the first $2^r$ Sobol' points of a $s$-dimensional sequence. Then, $B_0'$, $B_\ell$ and ${B'}_\ell$, for $\ell\geq 1$, are obtained from $B_0$ by carrying out digital shifts and scrambling operations. These operations guarantee that both $B_\ell$ and ${B'}_\ell$ inherit the $(t,r,s)$-net structure of the initial set $B_0$. We detail below the construction of $B_\ell$ and ${B'}_\ell$.
\bigskip

At step $\ell$, $\ell \geq 1$, $B_\ell=\{\vx_i^{(\ell)}\}_{i=0}^{2^r-1}$ is generated by applying a digital shift to $B_0$:

for each $i=0,\dots,2^r-1$, points $\vx_i^{(\ell)} = (x_{i,1}^{(\ell)},\dots,x_{i,s}^{(\ell)})^\intercal$ are obtained by:
\begin{equation}
\label{dig.shift}
(x_{i,j,1}^{(\ell)},\dots,x_{i,j,r}^{(\ell)})^\intercal = (x_{i,j,1}^{(0)},\dots,x_{i,j,r}^{(0)})^\intercal\oplus \ve_j,\qquad j= 1,\dots,s\, ,
\end{equation}
where $ x_{i,j}^{(\ell)}=\sum_{k = 1}^r x_{i,j,k}^{(\ell)}2^{-k}$ and $\ve_j=(e_{j,{0}},\dots,e_{j,{r-1}})^\intercal\in\mathbb{F}_2^r$.
\bigskip

Then, ${B'}_\ell=\{{\vx'}_i^{(\ell)}\}_{i=0}^{2^r-1}$ is obtained from $B_\ell$ by applying Tezuka's i-binomial scrambling \cite{Tezuka}. This scrambling operation writes as follows:

for each $i=0,\dots,2^r-1$, points ${\vx'}_i^{(\ell)} = ({x'}_{i,1}^{(\ell)},\dots,{x'}_{i,s}^{(\ell)})^\intercal$ are obtained by:
\begin{equation}
\label{ibinom.scrambling}
({x'}_{i,j,1}^{(\ell)},\dots,{x'}_{i,j,r}^{(\ell)})^\intercal = L_j^r (x_{i,j,1}^{(\ell)},\dots,x_{i,j,r}^{(\ell)})^\intercal,
\end{equation}
where $ {x'}_{i,j}^{(\ell)}=\sum_{k = 1}^r {x'}_{i,j,k}^{(\ell)}2^{-k}$ and each $L_j^r$ is a full rank lower triangular matrix of size $r \times r$ over $\mathbb{F}_2$.
\bigskip

%\item[Step 4.] The two blocks $B_l$ and ${B'}_l$ are then both randomized using the same Owen's scrambling column-wise.

>>>>

% The amssymb package provides various useful mathematical symbols
\usepackage{amsmath,amssymb}
\usepackage{graphicx}

@@

\newcommand{\fudge}{\fC}
\newcommand{\dtf}{\textit{\doubletilde{f}}}
\newcommand{\cube}{[0,1)^s}
\newcommand{\rf}{\mathring{f}}
\newcommand{\rnu}{\mathring{\nu}}
\newcommand{\natm}{\naturals_{0,m}}
\newcommand{\wcS}{\widecheck{S}}
\newcommand{\tol}{\text{tol}}
\newcommand{\bvec}[1]{\boldsymbol{#1}}
\newcommand{\vi}{\bvec{i}}
\newcommand{\vj}{\bvec{j}}
\newcommand{\ve}{\bvec{e}}
\newcommand{\vk}{\bvec{k}}
\newcommand{\vv}{\bvec{v}}
\newcommand{\vx}{\bvec{x}}
\newcommand{\vz}{\bvec{z}}
\newcommand{\dif}{\mathsf{d}}
\newcommand{\hf}{\hat{f}}
\newcommand{\hS}{\widehat{S}}
\newcommand{\tS}{\widetilde{S}}
\newcommand{\tf}{\tilde{f}}
\newcommand{\fC}{\mathfrak{C}}
\newcommand{\homega}{\widehat{\omega}}
\newcommand{\wcomega}{\mathring{\omega}}
\newcommand{\vzero}{\bvec{0}}
\newcommand{\integers}{\mathbb{Z}}
\newcommand{\naturals}{\mathbb{N}}
\newcommand{\ip}[3][{}]{\ensuremath{\left \langle #2, #3 \right \rangle_{#1}}}

@@

% use the thanksref command within \title, \author or \address for footnotes;
% use the ead command for the email address,
% and the form \ead[url] for the home page:
% \title{Title\thanksref{label1}}
% \thanks[label1]{}
% \author{Name\thanksref{label2}}
% \ead{email address}
% \ead[url]{home page}
% \thanks[label2]{}
% \address{Address\thanksref{label3}}
% \thanks[label3]{}
\selectlanguage{english}
\title{Iterative construction of replicated designs based on Sobol' sequences}
%\title{Replicated designs based on Sobol' sequences to estimate main effects of model inputs}
%\title{On the replication of Sobol' sequences to estimate main effects of model inputs}

@@

\begin{abstract}
\selectlanguage{english}
% Text of abstract in English
In the perspective of estimating main effects of model inputs, two approaches are studied to iteratively construct replicated designs based on Sobol' sequences. Space-filling properties of the resulting designs are studied based on two criteria.
{\it To cite this article: L.
Gilquin, Ll. A. Jim\'enez Rugama, E. Arnaud, F. J. Hickernell, H. Monod, C. Prieur, C. R. Acad. Sci. Paris, Ser. I 340 (2005).}

@@

\selectlanguage{francais}
% Text of abstract in French
\noindent{\bf R\'esum\'e} \vskip 0.5\baselineskip \noindent
{ \bf Construction de plans r\'epliqu\'es \`a partir de s\'equences de Sobol'.}
%{\bf Plans r\'epliqu\'es \`a base de s\'equences de Sobol' pour estimer les effets principaux des param\`etres d'un mod\`ele. }
Dans l'objectif d'estimer les effets principaux des param\`etres d'un mod\`ele, nous proposons d'\'etudier deux approches pour construire it\'erativement des plans r\'epliqu\'es \`a partir de s\'equences de Sobol'. Les propri\'et\'es de remplissement de l'espace des plans construits sont \'etudi\'ees sur la base de deux crit\`eres.
{\it Pour citer cet article~: L. Gilquin, Ll. A. Jim\'enez Rugama, E. Arnaud, F. J. Hickernell, H. Monod, C. Prieur, C. R. Acad. Sci.
Paris, Ser. I 340 (2005).}

@@

\section{Introduction}
Mathematical models often involve a substantial number of poorly known parameters. The effect of these parameters on the output of the model can be assessed through sensitivity analysis. Global sensitivity analysis methods are useful tools to identify the parameters having the most influence on the output. A well known approach is the variance based method introduced by Sobol' in \cite{Sobol2}. This method estimates sensitivity indices called Sobol' indices that summarize the influence of each model input. Among all Sobol' indices, one can distinguish first-order indices that estimate the main effect of each input.

The procedure proposed by Sobol' to estimate first-order Sobol' indices and its improvements (see Saltelli \cite{Saltelli} for an exhaustive survey) all suffer from a prohibitive cost of model evaluations that grows with respect to the input space dimension. %An elegant solution to reduce this cost relies on the construction of replicated designs introduced by McKay \cite{mckay}.  
 An elegant solution to reduce this cost relies on the construction of particular designs of experiments called replicated designs. The notion of replicated designs was first introduced by McKay through its introduction of replicated Latin Hypercubes in \cite{Mckay}. 
Below we define replicated designs in a wider framework:

\begin{definition}%[Replicated designs]
\label{rep.designs}
Denote by $\vx \in [0,1)^s$ a point with components $x_1,\dots,x_s$ and $\mathcal{D}=\{1,\dots,s\}$. Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in
$[0,1)^{s}$. Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp. $\mathcal{P}'^u$), $u \subsetneq \mathcal{D}$, denote the subset of dimensions of $\mathcal{P}$ (resp. $\mathcal{P}'$) indexed by $u$. We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a$ if $\forall \ u \subsetneq \mathcal{D}$ of cardinality $|u|=a$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ are the same point set in $[0,1)^a$.
\end{definition}

The replication procedure introduced in \cite{Mara,Tissot} allows to estimate all first-order Sobol' indices with only two replicated designs of order $1$. This procedure has the major advantage of reducing the estimation cost as the number of model evaluations (one design $\mathcal{P}$ of size $n$  and its replication $\mathcal{P}'$) becomes independent of the input space dimension. However, Sobol' indices estimates may still not be accurate enough if the input space is not properly explored.

\bigskip

In this note, we propose the construction of two replicated point sets based on Sobol' sequences that identify as two space-filling replicated designs of order $1$. These two designs ensure that the input space is properly explored and can be used within the replication procedure to estimate all main-effects of a numerical model. The construction of the two replicated designs is recursive, at each step each design is refined with a new set of points.

We first provide a brief introduction on digital sequences and then present two iterative approaches to construct the two replicated point sets. We end this note by studying the space-filling aspect of the two designs constructed.

@@

%The quality of any $(t,m,s)$-net or $(t,s)$-sequence is measured by $t$, called the $t$-value. The $t$-value is introduced in the $(t,m,s)$-net definition as follows:
$(t,m,s)$-nets are defined as follows:

@@

Thus, a $(t,m,s)$-net is defined such that all elementary intervals of volume at least $b^{t-m}$ will enclose a proportional number of points of $\mathcal{P}$, namely $b^{t-m}|\mathcal{P}|$ points. The most evenly spread nets are $(0,m,s)$-nets, since each elementary interval of the smallest volume possible, $b^{-m}$, contains exactly one point. The quality of any $(t,m,s)$-net is therefore measured by the parameter $t$, called $t$-value.

@@

$s$-dimensional Sobol' sequences are digital sequences designed in base $b=2$ and can be computed using the \emph{generating matrices}, a set of $s$ full rank infinite dimensional upper triangular matrices over the Galois field $\mathbb{F}_2:=\{0,1\}$. We will denote by $\oplus$ the addition in $\mathbb{F}_2$. These generating matrices are recursively constructed through primitive polynomials and initial directional numbers. In \cite{Kuo}, Kuo and Joe detail this construction and also suggest a particular choice for these matrices that optimize the 2 dimensional projection $t$-values.

Consider the generating matrices $C_1,\dots,C_s$, and $C_1^m,\dots,C_s^m$ their upper left corner blocks of size $m\times m$. Although $C_1,\dots,C_s$ are of infinite size, one only requires the knowledge of $C_1^m,\dots,C_s^m$ to construct the first $2^m$ points: for each $i=0,\dots,2^m-1$, the point $\vx_i = (x_{i,1},\dots,x_{i,s})^\intercal$ of the sequence is obtained dimension-wise by:
\begin{equation}
\label{dig.net.eq.}
(x_{i,j,1},\dots,x_{i,j,m})^\intercal = C_j^{m} \vi,\qquad j= 1,\dots,s\, ,
\end{equation}
where $x_{i,j} = \sum_{k \geq 1}^m x_{i,j,k}2^{-k}$ is the binary expansion of $x_{i,j}$ and $\vi = (i_{0},\dots,i_{m-1})^\intercal$ is the vector obtained from the binary expansion of $i= \sum_{k \geq 0}^{m-1} i_{k}2^{k}$. All matrix operations are performed in $\mathbb{F}_2$. Below we provide an example on how to compute $x_{11,1}=0.8125$ and $x_{9,2}=0.4375$,
\begin{equation*}
\begin{pmatrix}
x_{11,1,1} \\
x_{11,1,2} \\
x_{11,1,3} \\
x_{11,1,4}
\end{pmatrix} = 
\overbrace{
\begin{pmatrix}
1 & 0 & 0 & 0 \\
0 & 1 & 0 & 0 \\
0 & 0 & 1 & 0 \\
0 & 0 & 0 & 1
\end{pmatrix}}^{C_1^4}
\overbrace{
\begin{pmatrix}
1 \\
1 \\
0 \\
1
\end{pmatrix}}^{\bvec{11}}=
\begin{pmatrix}
1 \\
1 \\
0 \\
1
\end{pmatrix}
,\qquad
\begin{pmatrix}
x_{9,2,1} \\
x_{9,2,2} \\
x_{9,2,3} \\
x_{9,2,4}
\end{pmatrix} = 
\overbrace{\begin{pmatrix}
1 & 1 & 1 & 1 \\
0 & 1 & 0 & 1 \\
0 & 0 & 1 & 1 \\
0 & 0 & 0 & 1
\end{pmatrix}}^{C_2^4}
\overbrace{\begin{pmatrix}
1 \\
0 \\
0 \\
1
\end{pmatrix}}^{\bvec{9}} =
\begin{pmatrix}
0 \\
1 \\
1 \\
1
\end{pmatrix}
\end{equation*}
\bigskip

To compute the next $2^m$ points of the sequence, one can infer from Equation (\ref{dig.net.eq.}) that \\$(x_{i+2^m,j,1},\dots,x_{i+2^m,j,m+1})^\intercal=(x_{i+2^m,j,1},\dots,x_{i+2^m,j,m},0)^\intercal\oplus {(c_j^{m+1})}^\intercal$, where $c_j^{m+1}$ is the last column of $C_j^{m+1}$.

\begin{lemma}\label{Sobol_replicated}
All Sobol' sequences are digitally replicated of order 1.
\end{lemma}
\begin{pf*}{Proof.}
Consider any two $s$-dimensional Sobol' sequences generated by $C_1,\dots,C_s$ and $C'_1,\dots,C'_s$ respectively. Since any two matrices $C^{m}_j$ and ${C'}^{m}_j$ are square and full rank, the operations $\vi \mapsto C^{m}_j\vi$ and $\vi \mapsto {C'}^{m}_j\vi$ are one-to one and onto for all $i=0,\dots,2^m-1$. Therefore, they generate the same point sets.
\end{pf*}

@@

%\section{Iterative constructions of extensible replicated point sets of order 1}
\section{Iterative constructions of replicated point sets}

In this section we propose two different approaches to iteratively construct two replicated point sets, $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$, based on Sobol' sequences. These two constructions are carried out according to the following recursive scheme :
$$\left\lbrace \begin{array}{l}
\mathcal{P}_0= B_0 \\
\mathcal{P}_\ell= \mathcal{P}_{\ell-1} \cup B_\ell \end{array}\right. \,
\hspace*{0.5cm}
\left\lbrace \begin{array}{l}
\mathcal{P}'_0= {B'}_0 \\
\mathcal{P}'_\ell= \mathcal{P}'_{\ell-1} \cup {B'}_\ell \end{array}\right. 
$$
%$$\mathcal{P}_m= B_0 \cup \dots \cup B_m\, ,$$
%$$\mathcal{P}'_m= {B'}_0 \cup \dots \cup {B'}_m\, ,$$
where $B_\ell$ and $B'_\ell$, $\ell \geq 0$, are new sets of points added at step $\ell$ to refine $\mathcal{P}_{\ell-1}$ and $\mathcal{P}'_{\ell-1}$. For all $\ell$, $\mathcal{P}_\ell$ and $\mathcal{P'}_\ell$ are two replicated designs of order $1$.

The first approach is called multiplicative because $|P_\ell|=2^\ell$ while the second one with $|P_\ell|=\ell|B_0|$ is called additive. In the multiplicative case, we will directly use $2$ $s$-dimensional sequences as a result from Lemma \ref{Sobol_replicated}. However, for the additive case, we will consider an initial set of Sobol' points and apply different scramblings and digital shifts to extend the point sets. Additionally, in both cases one can randomize the points with Owen's scrambling \cite{OwenScrambling} as long as same coordinates of $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ share the same scrambling.

@@

Two replicated point sets of order 1 $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ can be constructed using two $s$-dimensional Sobol' sequences. We note $C_1,\dots,C_s$ the generating matrices used to generate $\mathcal{P}_\ell$ and ${C'}_1,\dots,{C'}_s$ those used to generate $\mathcal{P}'_\ell$. All these matrices need to be different.
% Our choice of the $2s$ generating matrices $C_1,\dots,C_s,{C'}_1,\dots,{C'}_s$ follows the results obtained by Joe and Kuo in \cite{Kuo}. These two authors proposed a set of generating matrices optimized based on the $t$-value of pairwise projections of the corresponding digital sequence. Here, we select $2s$ generating matrices from this set to generate our two designs $\mathcal{P}$ and $\mathcal{P}'$.
\bigskip

In order to recursively construct designs $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$, one just needs to compute $B_\ell=\{\vx_{2^{\ell-1}},\dots,\vx_{2^\ell-1}\}$ and ${B'}_\ell=\{\vx'_{2^{\ell-1}},\dots,\vx'_{2^\ell-1}\}$ at each step $\ell \geq 1$ to refine $\mathcal{P}_{\ell-1}$ and $\mathcal{P}'_{\ell-1}$, starting with $B_0=B'_0=\{\bvec{0}\}$ where $\bvec{0}$ denotes the null vector. Each set $B_\ell$ can be obtained applying equation (\ref{dig.net.eq.}) to $C_1,\dots,C_s$ and likewise for ${B'}_\ell$ using $C'_1,\dots,C'_s$.

@@

With the multiplicative approach, the size of designs $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ is multiplied by $2$ each time $\ell$ is increased by one. This growth rate may be inadequate for some applications. The additive approach presented in this section is attractive due to a slower size growth. Given an initial choice of $r\geq 1$ that specifies the size of $B_0$ and ${B'}_0$, only $|B_0|=2^r$ points are added to both designs at each step.

The main drawback of this approach is that $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ do not possess the structure of a Sobol' sequence anymore when $m\geq 1$. Still, both designs display good space-filling properties as shown in the next section.

\bigskip

The two replicated point sets $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ constructed with the additive approach are iteratively refined with $B_\ell$ and ${B'}_\ell$. Each $B_\ell$ and ${B'}_\ell$ are $(t,r,s)$-nets.

First, $B_0=\{\vx_i^{(0)}\}_{i=0}^{2^r-1}$ and ${B'}_0=\{{\vx'}_i^{(0)}\}_{i=0}^{2^r-1}$ are set to be the first $2^r$ Sobol' points of two $s$-dimensional sequences. Then, $B_\ell$ (resp. ${B'}_\ell$), for $\ell \geq 1$, is obtained from $B_0$ (resp. ${B'}_0$) by carrying out digital shifts and scrambling operations. These operations guarantee that both $B_\ell$ and ${B'}_\ell$ inherit the $(t,r,s)$-net structure of the initial sets $B_0$ and ${B'}_0$. We detail below the construction of $B_\ell$ and ${B'}_\ell$.
\bigskip

At step $\ell$, $\ell \geq 1$, $B_\ell=\{\vx_i^{(\ell)}\}_{i=0}^{2^r-1}$ is generated as follows:

for each $i=0,\dots,2^r-1$, points $\vx_i^{(\ell)} = (x_{i,1}^{(\ell)},\dots,x_{i,s}^{(\ell)})^\intercal$ are obtained by:
\begin{equation}
\label{dig.shift}
(x_{i,j,1}^{(\ell)},\dots,x_{i,j,r}^{(\ell)})^\intercal = L (x_{i,j,1}^{(0)},\dots,x_{i,j,r}^{(0)})^\intercal\oplus \ve_j,\qquad j= 1,\dots,s\, ,
\end{equation}
where $ x_{i,j}^{(\ell)}=\sum_{k = 1}^r x_{i,j,k}^{(\ell)}2^{-k}$, $\ve_j=(e_{j,{0}},\dots,e_{j,{r-1}})^\intercal\in\mathbb{F}_2^r$ and $L$ is a full rank lower triangular matrix of size $r \times r$ over $\mathbb{F}_2$.
\bigskip

Likewise ${B'}_\ell=\{{\vx'}_i^{(\ell)}\}_{i=0}^{2^r-1}$ is obtained as follows: 
%from $B_\ell$ by applying Tezuka's i-binomial scrambling \cite{Tezuka}. This scrambling operation writes as follows

for each $i=0,\dots,2^r-1$, points ${\vx'}_i^{(\ell)} = ({x'}_{i,1}^{(\ell)},\dots,{x'}_{i,s}^{(\ell)})^\intercal$ are obtained by:
\begin{equation}
\label{ibinom.scrambling}
({x'}_{i,j,1}^{(\ell)},\dots,{x'}_{i,j,r}^{(\ell)})^\intercal = {L'} ({x'}_{i,j,1}^{(0)},\dots,{x'}_{i,j,r}^{(0)})^\intercal\oplus {\ve'}_j,\qquad j= 1,\dots,s\, ,
\end{equation}
where $ {x'}_{i,j}^{(\ell)}=\sum_{k = 1}^r {x'}_{i,j,k}^{(\ell)}2^{-k}$, ${\ve'}_j=(e_{j,{0}},\dots,e_{j,{r-1}})^\intercal\in\mathbb{F}_2^r$ and ${L'}$ is a full rank lower triangular matrix of size $r \times r$ over $\mathbb{F}_2$.
\bigskip
